% Chapter Template

\chapter{Self-assessment on sustainability} % Main chapter title

\label{Chapter1}

During my studies, there have been different activities related with sustainability. It is a must that ICT\footnote{Information and communications technology} students know the effects of the solutions they will develop. 
ICT are currently releasing the 2\% of greenhouse gases\cite{Universidad2013} which is more than the aerospace industry. Not only this, the electronic waste is difficult to recycle and they end up in poor countries\cite{Ghana} condemning people to an unhealthy life.\\

This form\footnote{\href{goo.gl/kWLMLE}{Cuestionario de Estudiantes de Ingeniería Informática}} helped me to realize what are my strengths and weaknesses about sustainability: environment, economic, and social.\\

As explained before, we have a good education about sustainability and we are aware of ICT problems. I am very conscious with all the environmental problems ICT are causing because all the activities I have done in the past but I do not know how this problems can be solved at global level. I think it is a very hard problem and it has to be solved as soon as possible. On the other hand, I had not been aware about economic and social impact until some months ago. The moment when I understood that was when Uber appeared in Spain\cite{UberTaxi}. I am not going to discuss who was right but how a mobile application could affect the society and the economy (of the taxi collective in this case).\\

It is hard to predict which effects will have an ICT solution and I realized doing the form that it has not been my priority in my past projects. Do not misunderstand this, of course I want to improve the world with my projects but side effects are hard to predict. \\

In conclusion, I would say that I am conscious about the sustainability problems of ICT solutions but not how they can be solved. I am also not aware of the footprint of my past projects. 
