% Chapter Template

\chapter{Objectives} % Main chapter title

\label{Chapter1} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}

This project is an extension of a previous C++ library. The main goal of this project is to improve the time required to solve \emph{minimization} problems. To achieve this goal, the following objectives have been established. 

\section{General objectives}

\subsection{Pseudo-Boolean minimization}
Given some pseudo-boolean constraints ($c_{1}x_{1}+c_{2}x_{2}+\ldots +c_{n}x_{n} \leq k$) where $c_{i}$ and $k$ are integers and $x_{i}$ boolean variables, and a cost function, the goal is minimize it  $min(a_{1}x{1} + ... + a_{n}x_{n})$ in a way that all the restrictions are satisfied.


This project will try to reduce the time to solve these problems through two approaches:
\begin{itemize}
	\item Binary search:\\
	Implement the well known \emph{Binary Search}\footnote{Binary search is a search algorithm that finds the position of a target value within a sorted array. \href{https://en.wikipedia.org/wiki/Binary_search_algorithm}{(more)}} algorithm to find the minimum value for the cost function.
	\item Linear search:\\
	Some \emph{SAT Solvers} can learn and derive new restrictions from previous problems. To take advantage of this ability it is necessary to implement a \emph{Linear Search} algorithm.
\end{itemize}

\subsection{Timeout} 
For some problems, it is more important to find a solution before a deadline than finding the best possible solution. For instance, a delivery company must have all the route planned for all trucks before the journey starts, therefore, they care more about having a solution than finding the best one.\\
For this, a \emph{Timeout strategy} will be implemented in case that a good enough solution has been found or the problem does not seem to have one. 
\subsection{Multi-threading (optional)}
This tool will take advantage of multi-core processors trying to split the problem and solving each part separately.